Visualizations for the manuscript

### 2022-04-05 metanalysis_visualization/manuscript_Figures.Rmd
subgroup analysis

```{r Interrupted time series by sex}

patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_total %>% 
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  select(time_p, period, sex, count_sex, percentage, siteid)
# %>% 
#   inner_join(country_map)

bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map(~ bootstrapping_slopes(.x,
                                  group_name = .y,
                                  bootstrap_size = bootstrap_size,
                                  count = "count_sex", 
                                  percentage = "percentage"))

bootstrapped_coefficients_sex <- lapply(bootstrapped_sex, `[[`, 1) %>% bind_rows()
bootstrapped_fitted_sex <- lapply(bootstrapped_sex, `[[`, 2) %>% bind_rows()
```

```{r Interrupted time series by sex 2}
quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  # group_by(time_p, period, plotsLabel, sex) %>%
  group_by(time_p, period,  sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
```

```{r}
coefficients_df_sex <- patients_hospitalized_agg_sex_total %>% 
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
    mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)

```{r}
df_coefficients_boot_sex <- bootstrapped_coefficients_sex %>% 
  # left_join(coefficients_df_sex, by = c("plotsLabel", "sex"))
  left_join(coefficients_df_sex, by = c("sex"))
```

```{r}
names_sex <- unique(df_coefficients_boot_sex$sex)

@@

```{r bootstrap_plot}
ggplot(bootstrapped_fitted_sex, aes(x = time_p, y = predicted, group = interaction(iteration, period, sex))) +
  # facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=sex, color = interaction(period, sex)),
             alpha = 1) +
  scale_color_brewer(palette = "Paired") +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  # scale_colour_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df,
             aes(label=label),
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  # geom_label(data = plot_annotations_sex_df[["male"]],
  #            aes(label=label),
  #            x = -Inf,
  #            y = 15,
  #            hjust = 0,
  #            vjust = 0,
  #            size = 4,
  #           inherit.aes = FALSE) +
  # ylim(10, 90) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
  subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))
```
### Disorder group fix

@@

perc_disorder_group_total <- perc_disorder_group_complete %>%
  group_by( time_p, disorder_group ) %>%
  summarise( total_diagnoses = sum(count_icd, na.rm = TRUE),
             dg_cases = sum(count_dg),
             percentage = (dg_cases / total_diagnoses) * 100, 
             country = "ALL")

>>>>

#### Bootstrapping results by sex

```{r Interrupted time series by sex}
patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_total %>% 
  mutate(period = ifelse(time_p <= as.Date("2020-03-15"), "before_pandemic", "during_pandemic")) %>% 
  select(time_p, period, sex, count_sex, percentage, siteid)
# %>% 
#   inner_join(country_map)
```

```{r Interrupted time series by sex}
bootstrapped_sex <- patients_hospitalized_agg_sex_total %>%
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map(~ bootstrapping_slopes(.x,
                                  group_name = .y,
                                  bootstrap_size = bootstrap_size,
                                  count = "count_sex", 
                                  percentage = "percentage"))

bootstrapped_coefficients_sex <- lapply(bootstrapped_sex, `[[`, 1) %>% bind_rows()
bootstrapped_fitted_sex <- lapply(bootstrapped_sex, `[[`, 2) %>% bind_rows()
quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  # group_by(time_p, period, plotsLabel, sex) %>%
  group_by(time_p, period,  sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
coefficients_df_sex <- patients_hospitalized_agg_sex_total %>% 
  group_by(sex) %>% 
  # group_by(plotsLabel, sex) %>% 
    mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)

df_coefficients_boot_sex <- bootstrapped_coefficients_sex %>% 
  # left_join(coefficients_df_sex, by = c("plotsLabel", "sex"))
  left_join(coefficients_df_sex, by = c("sex"))
```

```{r annotation bootstrap disorder sex}
names_sex <- unique(df_coefficients_boot_sex$sex)

@@

```{r bootstrap_plot}
ggplot(bootstrapped_fitted_sex, aes(x = time_p, y = predicted, group = interaction(iteration, period, sex))) +
  # facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=sex, color = interaction(period, sex)),
             alpha = 1) +
  scale_color_brewer(palette = "Paired") +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  # scale_colour_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df,
             aes(label=label),
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  # geom_label(data = plot_annotations_sex_df[["male"]],
  #            aes(label=label),
  #            x = -Inf,
  #            y = 15,
  #            hjust = 0,
  #            vjust = 0,
  #            size = 4,
  #           inherit.aes = FALSE) +
  # ylim(10, 90) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
  subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))
```

### Disorder group

@@

perc_disorder_group_total <- perc_disorder_group_complete %>%
  group_by( time_p, disorder_group ) %>%
  summarise( total_diagnoses = sum(count_icd, na.rm = TRUE),
             dg_cases = sum(count_dg),
             percentage = (dg_cases / total_diagnoses) * 100, 
             country = "ALL", 
             siteid = "ALL") %>% 
  mutate(period = ifelse(time_p < pandemic_start_date,
                         "before_pandemic", 
                         "during_pandemic"))

#### Bootstrapping results by disorder groups

```{r}
disorders_to_select <- c(
  "Anxiety Disorders", 
  "Depressive Disorders", 
  "Feeding and Eating Disorders", 
  "Suicide or Self-Injury"
)

bootstrapped_disorders <- perc_disorder_group_total %>%
  filter(disorder_group %in% disorders_to_select) %>% 
  group_by(disorder_group) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
 group_map(~ bootstrapping_slopes(.x,
                                  group_name = .y,
                                  bootstrap_size = bootstrap_size,
                                  count = "dg_cases", 
                                  percentage = "percentage"))

bootstrapped_coefficients_disorder <- lapply(bootstrapped_disorders, `[[`, 1) %>% bind_rows()
bootstrapped_fitted_disorder <- lapply(bootstrapped_disorders, `[[`, 2) %>% bind_rows()
quantile_bootstrapped_fitted_disorder <- bootstrapped_fitted_disorder %>%
  # group_by(time_p, period, plotsLabel, sex) %>%
  group_by(time_p, period,  disorder_group) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
coefficients_df_disorder <- perc_disorder_group_total %>% 
  group_by(disorder_group) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))  %>% 
  group_modify(coefficient_slope_calculation) %>% 
  rename(observed_diff = estimate)

df_coefficients_boot_disorder <- bootstrapped_coefficients_disorder %>% 
  left_join(coefficients_df_disorder, by = c("disorder_group"))
```

```{r annotation boostrap disorders}
names_disorder <- unique(df_coefficients_boot_disorder$disorder_group)

plot_annotations_disorder <- df_coefficients_boot_disorder %>% 
  group_by(disorder_group) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_disorder) %>% 
  unlist()
plot_annotations_disorder_df <- data.frame(
  disorder_group = names(plot_annotations_disorder), 
  label = plot_annotations_disorder
)
```

```{r}
# plot_annotations_df <- plot_annotations_df %>%
#   left_join( country_map )

ggplot(bootstrapped_fitted_disorder,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_disorder,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_disorder[quantile_bootstrapped_fitted_disorder$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = filter(perc_disorder_group_total,
                           disorder_group %in% disorders_to_select),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
# ggsave("boostrapped_disorders.png", height = 20, width = 45, units = "cm")
